---
title: "Lab3_KessieSHEN"
format: html
editor: visual
---

# **1.Read in the data**

```{r}

download.file(
  "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
  destfile = file.path("~", "Downloads", "met_all.gz"),
  method   = "libcurl",
  timeout  = 60
)

met <- data.table::fread(file.path("~", "Downloads", "met_all.gz"))
met <- as.data.frame(met)
```

# \*\*2.Check the dimensions, headers, footers.

```{r}
dim(met)
head(met)
tail(met)
```

# \*\*3.Take a look at the variables.

```{r}
str(met)
```

# \*\*4.Take a closer look at the key variables.

```{r}
met <- data.table::fread(file.path("~", "Downloads", "met_all.gz"))
table(met$year)
table(met$day)
table(met$hour)
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
met[met$elev==9999.0] <- NA
summary(met$elev)
met <- met[met$temp > -40, ]
head(met[order(met$temp), ])
sum(is.na(met$wind.sp))
```

# \*\*5 Check the data against an external data source.

```{r}
met <- met[met$temp > -40, ]
head(met[order(met$temp), ])
```

location for the coldest temperature(-17.2C)， The coordinates (38.767, -104.3) refer to a location in Yoder, Colorado, which is situated east of Colorado Springs.

Does the range of values for elevation make sense? Why or why not?

In Yoder, Colorado, the average temperature in August typically ranges from about 15°C (59°F) at night to around 30°C (86°F) during the day.These data shows in August8(month8),so not very reasonable.

# \*\*6 Calculate summary statistics.

```{r}
elev <- met[which(met$elev == max(met$elev, na.rm = TRUE)), ]
summary(elev)
```

```{r}
cor(elev$temp, elev$wind.sp, use="complete")
```

## \[1\] -0.09373843

```{r}
cor(elev$temp, elev$hour, use="complete")
```

## \[1\] 0.4397261

```{r}
cor(elev$wind.sp, elev$day, use="complete")
## [1] 0.3643079
cor(elev$wind.sp, elev$hour, use="complete")
```

## \[1\] 0.08807315

```{r}
cor(elev$temp, elev$day, use="complete")
```

## \[1\] -0.003857766

#7 \*\*Exploratory graphs.

```{r}
hist(met$elev,col="red",)
hist(met$temp, col="orange", )
hist(met$wind.sp,col="green")
library(leaflet)
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)
library(lubridate)
elev$date <- with(elev, ymd_h(paste(year, month, day, hour, sep= ' ')))
summary(elev$date)
library(tidyverse)
# elev <- elev[order(elev$date), ]
head(elev)
```

```{r}
plot(elev$date, elev$temp, type="l")
plot(elev$date, elev$wind.sp, type="l")
```

The plot indicates that temperature peaks are higher in the latter part of August, gradually decreasing as September approaches.I think it maybe a seasonal transition?

# \*\*8.Ask questions

plot(elev$date, elev$temp, type="l", cex=. ),I tried different numbers in (cex=\_\_) the value is not changed, the size of the point changed,How should I understand this？
